Quality Definitions of Qualities

### 2019-12-18 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated more definitions

\subsection{\notdone{Installability} \oo{owner}}

\begin{defn}
  The capability of the software product to be installed in a specified
  environment \citep{ISO9126}.\citep{ISO9126}
\end{defn}

@@

The definition captures a vital metric of measure for this quality - effort, and
considers not just the installation but uninstallation and re-installation which
are all related toinstallation activities.  \oo{Done installability}

\subsection{\notdone{Correctness} \oo{owner}}

\begin{defn}  
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.  \wss{Is this verbatim from
    the original source?  If not, we should show those parts that are verbatim
    in quotes, so that readers know the parts that were developed by us.}
  \oo{Yes, verbatim}

@@

\begin{defn}
  According to \citet{wilson2009quality}, the degree to which a system is free
  from defects in its specification, design, and implementation, is its
  correctness.  \wss{Olu, can you please rephrase this one to match how the
    other definitions are presented.  That is, give the verbatim definition
    followed by the citation.}
\end{defn}

@@

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked with Mccall}
\end{defn}

\begin{defn} \label{Correctness_Selected} 
  The degree to which a system or component is free from faults in its
  specification, design and implementation \citep{IEEEComputerDictionary1991}.
\end{defn}

@@

Definition~\ref{Correctness_Selected}: The degree to which a system or component
is free from faults in its specification, design and implementation.  \wss{I
  think I prefer the Ghezzi definition, but with respect to all requirements
  (not just functional).}

@@

To determine whether a program is correct, we must be able to refer to both its
specification, design and implementation to understand the intended purpose and
based on defined metrics, determine the extent to which this is met. Most
definitions of correctness refers only to functional specifications but this
definition is broad and is able to capture both functional and non-functional
specification without explicitly specifying it.\oo{We could modify the
  definition to explicitly state functional and non-functional if we decide.}
There is no direct tool or method for measuring correctness. One way of building
confidence in correctness is by reviewing to ensure that each requirement stated
is one that the stakeholders and experts desire.  By maintaining traceability,
consistency and unambiguity, we can reduce the occurrence of errors and make the
goal of reviewing for correctness easier.

The quality of a software's operation is dependent on the degree of correctness
\citep{berander2005software}. Correctness and reliability are said to have
dependencies, such that if a system exhibits a high degree of correctness then
it tends to be reliable \citep{GhezziEtAl2003}. \oo{Done Correctness}

\wss{We probably do not need the extra bits about measuring correctness and the
  dependency between correctness and other qualities.  We can discuss how to
  measure correctness as the next exercise we are doing after concluding the
  definitions exercise.  If the tradeoffs between qualities are important, we
  should cover that in a more systematic way.}

@@

\begin{defn}
  A software is verifiable if its properties can be verified easily
  \citep{GhezziEtAl2003}.  \wss{Is this a direct quote?}
\end{defn}

\begin{defn} \label{Defn_Verifiability1}
  Attributes of software that relate to the effort needed for validating the
  modified software \citep{iso2001iec}.
\end{defn}

\begin{defn}
  Effort required to test a program to ensure that it performs its intended
  function \citep{McCallEtAl1977}. (As summarized in
  \citet{pressman2005software})\oo{McCall defined this as testability not verifiability}
\end{defn}

\begin{defn}
	The effort required to test a program to ensure that it performs its
	intended function \citep{McCallEtAl1977}. (As summarized in
	\citet{VanVliet2000}.) \oo{similar to \citep{pressman2005software}, this}
\end{defn} \oo{McCall defined this as testability not verifiability}

@@

Combined definitions~\ref{Defn_Verifiability1}
rephrased: Testability or verifiability is the degree to which a system or
component facilitates the establishment of test criteria and the performance of
tests to determine whether those criteria have been met and the effort required
to test.

@@

Definition is concise and measurable.  Verifiability involves solving the
equations right \citep[p.~23]{Roache1998}; it benefits from rational
documentation that systematically shows, with explicit traceability, how the
governing equations are transformed into code.  \oo{Verifiability is sometimes
  referred to as testability, so I culled some testability definitions and added
  here} \wss{culled means removed - is that your intention?} \oo{culled could
  also mean 'to choose', so I meant, I choose from some definitions of
  testability and added to the list}

@@

\begin{defn}
  Validatability of a software is the degree of ease in validating (checking)
  that software meets user needs. \wss{Need a citation} \oo{To be removed, I
    don't have any citation, definition was modified from the definition of
    verifiability}
\end{defn}

\begin{defn}
  Validatability means solving the right equations \citep[p.~23]{Roache1998}.
  \oo{Validation?}  \wss{We should also have the definition for verification
    about solving the equations right.}
\end{defn}

\begin{defn} \label{Validatability_Selected} 
  Validation is the process of evaluating software during or at the end of the
  development process to determine whether it satisfies specified business
  requirements \citep{softwaretestingfundamentals}.  \wss{Please use the
    author's name for this citation.  If that isn't known, use the name of the
    organization that published this material.}
\end{defn}

\begin{defn}
  Validation refers to a different set of tasks that ensure that the software
  that has been built is traceable to customer requirements.
\end{defn}

@@

\begin{defn}
  Software validation checks that the software product satisfies or fits the
  intended use (high-level checking), i.e., the software meets the user
  requirements, not as specification artifacts or as needs of those who will
  operate the software only; but, as the needs of all the stakeholders (such as
  users, operators, administrators, managers, investors, etc.)
   \wss{This reference is not appearing in the Reference
    list.  We also don't really want a Wikipedia citation in a scholarly paper.
    Can you please find the source where this definition originally came from?}
\end{defn}

@@

Validatability is improved by a rational process via clear documentation of the
theory and assumptions, along with an explicit statement of the systematic steps
required for experimental validation. It is entirely possible that a product
passes when verified but fails when validated. This can happen when, say, a
product is built as per the specifications but the specifications themselves
fail to address the user’s needs

@@

\begin{defn}
  A set of attributes that relate to the capability of software to maintain its
  level of performance under stated conditions for a stated period of time
  \citep{iso2001iec}. (As summarized in \citet{berander2005software}.)
  \wss{This definition does not match the definition I found in the
    \cite{ISO9126}.  @olu, can you please look into this?  My definition is
    given below.  Also, I've added a pdf of the ISO standard to the pub repo.}
\end{defn}

>>>>

\subsection{{Installability} \oo{owner}}

\begin{defn}
  The capability of the software product to be installed in a specified
  environment \citep{ISO9126}.
\end{defn}

@@

 The definition captures a vital metric of measure for this quality - effort, and considers not just the installation but uninstallation and re-installation which are all related to installation activities.  \oo{Done installability}

\subsection{{Correctness} \oo{owner}}

\begin{defn} \label{Correctness_Selected}
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.   \wss{Is this verbatim from the original source?  If not, we should show those parts that are verbatim in
  quotes, so that readers know the parts that were developed by us.}
  \oo{Yes, verbatim}

@@

\begin{defn}
  The degree to which a system is free from defects in its specification, design, and implementation, is its correctness \citep{wilson2009quality}.  \oo{Need to verify this definition, still searching for this paper}
\end{defn}

@@

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked with pdf}
\end{defn}

\begin{defn}  
  The degree to which a system or component is free from faults in its
  specification, design and implementation \citep{IEEEComputerDictionary1991}.
\end{defn}

@@

Definition~\ref{Correctness_Selected} rephrased: A program is functionally correct if it behaves according to its stated specifications  \oo{Proposed definition updated to Ghezzi's}

@@

To determine whether a program is correct, we must be able to refer to both its
specification, design and implementation to understand the intended purpose and
this definition captures it all.

@@

\begin{defn}
	Verification involves solving the equations right \citep[p.~23]{Roache1998}.
\end{defn}

\begin{defn}
  A software is verifiable if its properties can be verified easily
  \citep{GhezziEtAl2003}.  \wss{Is this a direct quote?} \oo{yes}
\end{defn}

\begin{defn} \label{Defn_Verifiability1}
Verifiability ``means that you should be able to write a set of tests that can demonstrate that the delivered system meets each specified requirement'' \citep{sommerville}.	
\end{defn}

@@

Definition~\ref{Defn_Verifiability1}:
Verifiability means that you should be able to write a set of tests that can demonstrate that the delivered system meets each specified requirement.

@@

Definition is concise and measurable.  Verifiability involves solving the
equations right \citep[p.~23]{Roache1998}.

@@

\begin{defn}
  Validation means solving the right equations \citep[p.~23]{Roache1998}.
\end{defn}

\begin{defn} \label{Validatability_Selected} 
  Validation is the process of evaluating software during or at the end of the
  development process to determine whether it satisfies specified business
  requirements \citep{softwaretestingfundamentals}.  \wss{Please use the
  author's name for this citation.  If that isn't known, use the name of the
  organization that published this material.} \oo{This is a weblink, that's the organization's name I guess}
\end{defn}

\begin{defn}
  Validation refers to a different set of tasks that ensure that the software
  that has been built is traceable to customer requirements.{to be removed, its from geeksforgeeks}
\end{defn}

@@

\begin{defn}
  Software validation checks that the software product satisfies or fits the
  intended use (high-level checking), i.e., the software meets the user
  requirements, not as specification artifacts or as needs of those who will
  operate the software only; but, as the needs of all the stakeholders (such as
  users, operators, administrators, managers, investors, etc.)
  \wss{This reference is not appearing in the Reference
  list.  We also don't really want a Wikipedia citation in a scholarly paper.
  Can you please find the source where this definition originally came from?}\oo{Could not find a different source from Wikipedia}
\end{defn}

@@

@@
